A word-sense representation for documents based on information value and word sense disambiguation

### 2014-03-19 paper/refactor.tex
Paragraph added.

For ``Imperialism ... '', we suffered the appearance of a very general sense (universe.n.01) which made a nonrelated sense as hair to appear second in the ranking. Also, a very characteristic concept of the  as \textbf{capitalism} appears unrelated, because it is not very close (in the hypernyms/hyponyms taxonomy) to the top senses of this work. ``Materialism ... '' had the same problem but the other way around: \textbf{revolution} was just very close to \textbf{experience}, but had nothing to do with the text in general.

@@

\section{Conclussion \& Future work}
The original scope of this investigation was the definition of a measure of distance between the works of a whole year but we find a lot of complexities in the definition of that model. While we decide to reduce the scope of this work for mental health, we consider the metric defined in this article as a step into the concretion of the original goal.

>>>>

In ``Imperialism ... '', we suffered the appearance of a very general sense (universe.n.01) which made a nonrelated sense as hair to appear second in the ranking. Also, a very characteristic concept of the  as \textbf{capitalism} appears unrelated, because it is not very close (in the hypernyms/hyponyms taxonomy) to the top senses of this work. ``Materialism ... '' had the same problem but the other way around: \textbf{revolution} was just very close to \textbf{experience}, but had nothing to do with the text in general.

Many of these problems come from the fact that path similarity is not a good measure of semantic similarity. Of course, two senses which have a high path similarity are similar (they are very close in terms of hypernyms/hyponyms), but the other way round is not valid. For instance, meronimy is not taken into account in this metric.

@@

\section{Conclussion \& Future work}
The original scope of this investigation was the definition of a measure of distance between the works of a whole year and a concept; so we could measure whether the literary production of Lenin in some year was close to ``revolution'', ``theory'', etc.
